### 2014-04-09 brains-protocol.tex
Add a section on the global evolution of quotation families

\subsection{Detection of transformations}

@@

We face an inference problem where, given all quotations and their occurrence timestamps, we must estimate which was the originating quotation for each instance of each quotation.
We therefore model the underlying quotation selection process by making a few additional assumptions which let us define quote-to-quote transformations and substitutions from the available data.

@@

\subsection{Global evolution of quotation families}

\subsection{Transformation process}

We then focus on the transformation process at work when authors reproduce quotations, by examining the features of substituted and substituting words in each substitution.
Note that since we only consider substitutions and not faithful copies, we measure the features of an alteration \emph{knowing that there has been an alteration}, and we do not take invariant quotations into account.
Indeed, in the first case we know there has been a human reformulation, whereas in the second case it is impossible to know whether there has been perfect human reformulation or simply digital copy-pasting of a source (``{\sc Ctrl-C}/{\sc Ctrl-V}'').

>>>>

\subsection{Detection of substitutions}

@@

We face an inference problem where, given all quotations and their occurrence timestamps, we must estimate which was the originating quotation for each instance of each quotation.
We therefore model the underlying quotation selection process by making a few additional assumptions which let us define quote-to-quote substitutions from the available data.

@@

\subsection{Long-term evolution of quotation families}

We first examine the evolution of quotation families under the repeated action of substitutions.
Our goal in this step is to identify the long-term effect of cognitive bias over the lifetimes of quotation families and thus over the framing of public information.

\rk{on pourrait en fait modéliser et formaliser ça de façon bien poussée en allant chercher du côté de l'analyse des séries temporelles et des processus stochastiques en général, mais bon...
c'est pas le but ici, et ça serait une toute autre recherche, et un autre public.
Oder?}

A discreet time (as explained in the discreet-time models in the previous section) is best suited to observe this: we first slice each quotation family into a number of time bags, each bag $\mathcal{B}_n$ containing all the quotations that appear in its corresponding time interval $\left[ t_n, t_{n + 1} = t_n + \Delta t \right[$ (where $\Delta t$ is a number of days, 1 to 5 in practice).
Each quote in a time bag is counted as many times as it occurs in the corresponding time interval.

We then compute the distribution of word features for each time bag $\mathcal{B}_n$ of each quotation family, and sum those distributions over all quotation families.
This yields a distribution of feature values for each $n$, which is the simplest possible view of the state of an average quotation family in its $n$-th time bag, i.e. after $n \times \Delta t$ days.\footnote{For consistency, if we do this for $n$ going up to $N$, we only include quotation families that span long enough to have at least $N$ time bags.}
Such a computation makes no assumptions on the way quotations undergo substitutions over time.

The raw distributions built with this computation are stationary.
\rk{figure/stats à l'appui ?
bouger ça dans les résultats ?
ou le garder comme ça, mentionné en passant pour justifier la suite ?}
That is, the substitutions on quotations over time have no global effect on quotation families, either because external quotations are continuously fed into the family and compensate for the effect of substitutions, or because substitutions operate on a marginal portion of the quotation families, or both.

\bigskip
To narrow this view to the specific effects of cognitive bias we consider substitution \emph{chains}: after selecting one of the discreet-time substitution detection models (see previous section), we filter time bags to include only new quotes produced by substitutions themselves based on quotes produced by substitutions, and so on recursively.
The first time bag is therefore untouched, the second contains the quotations produced by substitutions from the first, the third by substitutions from the second, and so on.
We thus observe only the repeatedly-affected portion of the quotation families, and obtain a simple view of the action of repeated cognitive bias.

\subsection{Substitution process}

We then focus on the individual substitution process at work when authors transform quotations, by examining the features of the substituted and substituting words in each substitution.
Note that since we only consider substitutions and not faithful copies, we measure the features of an alteration \emph{knowing that there has been an alteration}, and we do not take invariant quotations into account.
Indeed, in the first case we know there has been a human reformulation, whereas in the second case it is impossible to know whether there has been perfect human reformulation or simply digital copy-pasting of a source (``{\sc Ctrl-C}/{\sc Ctrl-V}'').

### 2014-04-09 brains-results.tex
Add a section on the global evolution of quotation families

>>>>

\TB{Results for global evolution of features:}

\TB{1/ no effect on global distribution => either continuous reinjection with base distribution, or substitutions are marginal (we can't separate those two with the information we have), or they are on marginal quotations (but no, because in that case we would see a difference when dropping quote frequency, which we don't).
So the global distribution is stationary.}

\TB{2/ we do see an effect when looking at chains, i.e. restricting the source quotes to be the product from previous step.}

\TB{3/ also no effect when allowing more complex transformations than 1-word substitutions => they are either reinjections, or the process is not as constrained as 1-word substitutions.}
